What can Issues on GitHub and Google Code tell us about Bug Hazards in Android and Java?

### 2015-02-14 android-stacks.tex
Added reference to paper on crashes in distributed systems.
From paper:

We found the majority of catastrophic failures could easily have been prevented by performing simple testing on error handling code

https://www.usenix.org/conference/osdi14/technical-sessions/presentation/yuan

Studies have shown that exception-related code is generally poorly understood and among the least tested parts of the system~\cite{miller1997issues,Robil00,shah2010understanding, 
garcia2007extracting,garcia2001comparative,cabral2007exception,coelho2011unveiling}.
As a consequence they may inadvertently negatively affect the system: exception-related code may introduce failures such as 
uncaught exceptions~\cite{jo2004uncaught, Zhang12} - 
which can lead to system crashes, making the system even less robust~\cite{coelho2011unveiling}.

>>>>

Studies have shown that exception-related code is generally poorly understood and among the least tested parts of the system~\cite{miller1997issues,Robil00,shah2010understanding, 
garcia2007extracting,garcia2001comparative,cabral2007exception,coelho2011unveiling,yuan:2014.osdi}.
As a consequence they may inadvertently negatively affect the system: exception-related code may introduce failures such as 
uncaught exceptions~\cite{jo2004uncaught, Zhang12} - 
which can lead to system crashes, making the system even less robust~\cite{coelho2011unveiling}.
